Spatial Analysis

### 2022-09-19 Scripts/spatial_analisis.Rmd
Fixed threshold mess 75trh to 25

# Visual exploration (o.k! )
ggplot(land_sf) +
  geom_sf(aes(fill = state)) +
  scale_fill_manual(values = state_pallet) +
  theme_dark()

@@

# quantiles_df <- overall_port_data %>% 
#   group_by(species_name) %>% 
#   summarise(
#     "95th" = quantile(year_ton, 0.95),
#     "75th" = quantile(year_ton, 0.75),
#     "50th" = quantile(year_ton, 0.50)) %>% 
#   gather("tresh","quant",`95th`:`50th`)
# 
# 
# top_portsb <- overall_port_data %>% 
#   left_join(quantiles_df,
#             by = "species_name") %>% 
#   mutate(
#     treshold = ifelse(year_ton >= quant,tresh,NA) 
#   )

top_ports <- bind_rows(
  # 75th percentile used in project
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.25,year_ton) %>%  # top 75
    mutate(tresh = "75th"),
  # -------------------- #
  # For sensitivity values
  # -------------------- #
  # 95%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.05,year_ton) %>%  
    mutate(tresh = "95th"), # top 95
  # 85%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.15,year_ton) %>% 
    mutate(tresh = "85th"), # top 85
  # 65%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.35,year_ton) %>%  # top 75
    mutate(tresh = "65th"),
  # 50%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.5,year_ton) %>%  # top 50
    mutate(tresh = "50th")
)

@@

port_map <- noaa_ports_complete %>%  
  filter(tresh == "75th")

@@

# Visual exploration of all together (o.k! )
ggplot() +
  geom_sf(data = eez_sf, aes()) +
  geom_sf(data = land_sf, aes(fill = state), alpha = 0.3) +
  geom_sf(data = state_sf, aes(color = state), fill = NA) +
  geom_point(data = subset(noaa_ports_complete, tresh == "75th"), aes(x = lon, y = lat,
                                                                      shape = species_name), size = 3, alpha = 0.7) +
  scale_color_manual(values = state_pallet) +
  scale_fill_manual(values = state_pallet) +
  theme_dark() +
  coord_sf(ylim = c(33,48))

@@

#Load top port data 
ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th")

@@

# Ports data
ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th") %>%
  group_by(species_name,state_postal) %>% 
  summarise(n =n()) %>% 
  select(-n)
# distinct(c(,state_postal), .keep_all = T) # No need for duplication

@@

my_path("D","Partial","top_ports.csv", read = T) %>% 
  filter(tresh == "75th",
         state_postal == "NY") %>% 
  ggplot() +
  geom_point(
    aes(
      x = lon,
      y = lat,
      color = port_name
    )
  )

>>>>

# Visual exploration (o.k! )
# Visual exploration (o.k! )
ggplot() +
  geom_sf(data = st_as_sf(map("state", plot = FALSE, fill = TRUE))) +
  geom_sf(data = land_sf, aes(fill = state)) +
  scale_fill_manual(values = state_pallet) +
  my_ggtheme_m(leg_pos = "right")

@@

# quantiles_df <- overall_port_data %>% 
#   group_by(species_name) %>% 
#   summarise(
#     "95th" = quantile(year_ton, 0.95),
#     "12th" = quantile(year_ton, 0.75),
#     "50th" = quantile(year_ton, 0.50)) %>% 
#   gather("tresh","quant",`95th`:`50th`)
# 
# 
# top_portsb <- overall_port_data %>% 
#   left_join(quantiles_df,
#             by = "species_name") %>% 
#   mutate(
#     treshold = ifelse(year_ton >= quant,tresh,NA) 
#   )

top_ports <- bind_rows(
  # Top 25 % used in this project
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.25,year_ton) %>%  # top 25 %
    mutate(tresh = "25th"),
  # -------------------- #
  # For sensitivity values
  # -------------------- #
  # 5%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.05,year_ton) %>%  
    mutate(tresh = "5th"), # top 5%
  # 15%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.15,year_ton) %>% 
    mutate(tresh = "15th"), # top 15%
  # 35%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.35,year_ton) %>%  # top 35%
    mutate(tresh = "35th"),
  # 50%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.5,year_ton) %>%  # top 50 %
    mutate(tresh = "50th")
)

@@

port_map <- noaa_ports_complete %>%  
  filter(tresh == "25th")

@@

# Visual exploration of all together (o.k! )
ggplot() +
  geom_sf(data = eez_sf, aes()) +
  geom_sf(data = land_sf, aes(fill = state), alpha = 0.3) +
  geom_sf(data = state_sf, aes(color = state), fill = NA) +
  geom_point(data = subset(noaa_ports_complete, tresh == "12th"), aes(x = lon, y = lat,
                                                                      shape = species_name), size = 3, alpha = 0.7) +
  scale_color_manual(values = state_pallet) +
  scale_fill_manual(values = state_pallet) +
  theme_dark() +
  coord_sf(ylim = c(33,48))

@@

#Load top port data 
ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "12th")

@@

# Ports data
ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "12th") %>%
  group_by(species_name,state_postal) %>% 
  summarise(n =n()) %>% 
  select(-n)
# distinct(c(,state_postal), .keep_all = T) # No need for duplication

@@

my_path("D","Partial","top_ports.csv", read = T) %>% 
  filter(tresh == "12th",
         state_postal == "NY") %>% 
  ggplot() +
  geom_point(
    aes(
      x = lon,
      y = lat,
      color = port_name
    )
  )
